Example output from simulations for MBNL1 where Va = 0

### 2020-01-27 null_replication/scripts/mbnl1_analysis.rmd
upd

>>>>

## Other plots

Histograms of F values for fast and R versions

```{r}
hist(b$r_f4)
hist(b$fast_f4)
```

Is the rs13069559 more correlated with the rest of the genome than expected by chance?

Summary of rs13069559

```{r}
r_rs13069559 <- cor(mat[,1], mat[,-1])
median(r_rs13069559)
hist(r_rs13069559)
```

Choose some random snps, get median LD r of each SNP against all other SNPs

```{r}
set.seed(1)
snps <- sample(1:ncol(mat), 32, replace=FALSE)

rval <- mclapply(1:length(snps), function(x)
{
	r_rand <- cor(mat[,snps[x]], mat[,-snps[x]])
	return(median(r_rand))
}, mc.cores=16)
```

Plot median r values

```{r}
library(ggplot2)
o <- data.frame(what = c("rs13069559", rep("random", length(snps))), median_r = c(median(r_rs13069559), unlist(rval))) %>%
	arrange(median_r) %>%
	mutate(ord = 1:n())

ggplot(o, aes(x=ord, y=median_r)) +
geom_point(aes(colour=what))
```

Looks like the median LD across the genome of rs13069559 is pretty high.
